Investigating the outer reaches of the Sculptor and Ursa Minor dwarf galaxies

### 2025-07-23 thesis/discussion.tex
refining intro

\begin{itemize}
\tightlist
\item
  disk galaxy formation \citet{fall+efstathiou1980}, \citet{mestel1963}
\end{itemize}

@@

@@

\begin{itemize}
\tightlist
\item
  \citet{benitez-llambay+2016}
\item
  \citet{mercado+2021}: formation of metallicity gradients from SFH
\item
  \citet{revaz+jablonka2018} natural formation of multi-component and
  gradients from cosmological simulations of dwarf galaxies. Originate
  from dynamical heating of metal rich population and outside in star
  formation?
\item
  \citet{el-badry+2016}. Feedback drives fluctuations in size + radial
  migration =\textgreater{} population gradients.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \citet{arronyo-polonio+2024}
\item
  \citet{pace+2020}
\item
  \citet{fabrizio+2016}, \citet{kordopatis+2016} (multi-component in
  Carina)
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  disk galaxy formation \citet{fall+efstathiou1980}, \citet{mestel1963}
\item
  valcke+derijcke+dejonghe2008 with early idealized hydro simulations
  show Sérsic values from simulations between 0.8 and 1 for dSph,
  indicating a natural formation of Exponential or slightly steeper
  density profiles.
\end{itemize}

@@

\subsection{Alternatives to exponential
profiles}\label{alternatives-to-exponential-profiles}

\begin{itemize}
\tightlist
\item
  elmegreen+hunter2006: Discuss the formation of double exponentials in
  disk galaxies. While a simpler idealized / Semi-analytic model of star
  formation, show that assuming exponentail gas and KS-relation with SF
  threshhold, that reduction of turbulance (driven by a number of
  processes) in outer disk leads to a steeper decline in SFR as crossing
  the critical SF threshold becomes less likely.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \citet{benitez-llambay+2016}
\item
  \citet{mercado+2021}: formation of metallicity gradients from SFH
\item
  \citet{revaz+jablonka2018} natural formation of multi-component and
  gradients from cosmological simulations of dwarf galaxies. Originate
  from dynamical heating of metal rich population and outside in star
  formation?
\item
  \citet{el-badry+2016}. Feedback drives fluctuations in size + radial
  migration =\textgreater{} population gradients.
\item
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \citet{arronyo-polonio+2024}
\item
  \citet{pace+2020}
\item
  \citet{fabrizio+2016}, \citet{kordopatis+2016} (multi-component in
  Carina)
\item
  \citet{battaglia+2006}, \citet{amorisco+evans2012} for fornax
\end{itemize}
